---
title: "Identifying home locations for users"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE)
library(sf)
library(tidyverse)
library(lubridate)
library(here)
```

## Identifying home locations for users 

To identify home locations for users, we use four built-in recipes from `homelocator` package. 

```{r eval=TRUE, message=TRUE}
library(homelocator)
```


### Load de-identified dataset 

```{r}
df <- read_csv(here("analysis/data/derived_data/deidentified_sg_tweets.csv")) %>% #load de-identified dataset
  mutate(created_at = with_tz(created_at, tzone = "Asia/Singapore")) # the tweets were sent in Singapore, so must convert the timezone to SGT, the default timezone is UTC! 
```


### Recipe: APDM

Recipe 'APDM' (Rein Ahas et al., 2010) calculates both the average and standard deviation timestamps in each location for each user. 

```{r apdm}
#must load neighbors when using APDM recipe 
df_neighbors <- readRDS(here("analysis/data/derived_data/neighbors.rds"))
hm_apdm <- identify_location(df, user = "u_id", timestamp = "created_at", location = "grid_id", 
                             tz = "Asia/Singapore", keep_score = F, recipe = "APDM")
```


### Recipe: FREQ

Recipe 'FREQ' simply selects the most frequently ‘visited’ location as users' home locations. 

```{r freq}
hm_freq <- identify_location(df, user = "u_id", timestamp = "created_at", location = "grid_id", 
                             tz = "Asia/Singapore", show_n_loc = 1, recipe = "FREQ")
```

### Recipe: HMLC

Recipe ‘HMLC’ weighs data points across multiple time frames to ‘score’ potentially meaningful locations. 


```{r hmlc}
hm_hmlc <- identify_location(df, user = "u_id", timestamp = "created_at", location = "grid_id", 
                             tz = "Asia/Singapore", show_n_loc = 1, keep_score = F, recipe = "HMLC")
```

### Recipe: OSNA

Recipe 'OSNA' (Efstathiades et al., 2015), only considers data points sent on weekdays and divides a day into three time frames - ‘rest time’, ‘leisure time’ and ‘active time’. The algorithm finds the most ‘popular’ location during ‘rest’ and ‘leisure’ time as the home locations for users. 


```{r osna}
hm_osna <- identify_location(df, user = "u_id", timestamp = "created_at", location = "grid_id", 
                             tz = "Asia/Singapore", show_n_loc = 1, recipe = "OSNA")
```


The identified homes are in `analysis/data/derived_data`.

```{r}
write_csv(hm_apdm, path = here("analysis/data/derived_data/hm_apdm.csv"))
write_csv(hm_freq, path = here("analysis/data/derived_data/hm_freq.csv"))
write_csv(hm_hmlc, path = here("analysis/data/derived_data/hm_hmlc.csv"))
write_csv(hm_osna, path = here("analysis/data/derived_data/hm_osna.csv"))
```

